Untitled

### 2024-10-17 code/manuscript_altanalysis.Rmd
Distance Instrument

df.temptemp <- df.mt %>% 
    rename(ID = ID.x) %>% 
    group_by(ID) %>% 
  mutate(Closed = ifelse(lead(is.na(Sites)), 100, 0)) %>% 
  select(ClinicHHI, Att, `BHCMIS ID`, value, ID, MS, Year, Pct.NHA:Pct.Homeless, Qcomp, Total, Altman, logPatsPerStaff, 
         htn.rate, dm.rate, pap.rate, crc.rate, childbmi.rate, adultbmi.rate, Complexity, Intensity, Pct.MCD, Pct.MCR, Pct.COM, Pct.None, CostPerPat, quick_ratio, months_of_cash, Profitability, LiabPctAssets, Staff, Closed) %>% 
  unique()

@@

@@

  df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx))
  colnames(df.temptemptemp)[(16+k)] <- "Outcome"
  model <- feols(Outcome ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless   | I((10000 - ClinicHHI)/1000) ~ Tx + factor(Year) + factor(ID) , cluster = "ID", data = df.temptemptemp)

  coeffs <- rbind(coeffs, model$coeftable[2,])

@@

core.iv.estimates <- data.frame(cbind(colnames(df.temptemp)[17:38], (coeffs[-1,]))) %>% 
  #select(V1, Estimate, Pr...t.., Estimate.1, Pr...t...1) %>% 
  mutate(Estimate = round(as.numeric(Estimate), 2), `95% CI` = paste(round(as.numeric(Estimate) - 1.96 * as.numeric(`Std..Error`), 2), ", ", round(as.numeric(Estimate) + 1.96 * as.numeric(`Std..Error`), 2), sep = "")) %>% 
  select(V1, Estimate, `95% CI`)

@@

model <- feols(Complexity ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless   | I((10000 - ClinicHHI)/1000) ~ Tx  + factor(Year) + factor(ID), cluster = "ID", data = df.temptemp)
summary(model)

model <- lm(data = df.temptemp, Pct.None ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless   + Tx + factor(Year) + factor(ID) )
summary(model)

@@

```{r}
 did2s(
      data = df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)  )   , 
      yname = "Complexity", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = TRUE
    )

 event_study(data = df.temptemp ,
  yname = "ClinicHHI", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>%
  filter(abs(term) <= 6) %>%
  #filter(estimator == "Gardner (2021)") %>%
  #filter(estimator == "Callaway and Sant'Anna (2020)") %>%
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("FirstStage: ") + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")

@@

  df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx))
  colnames(df.temptemptemp)[(16+k)] <- "Outcome"
  model <-  did2s(
      data = df.temptemptemp, 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = TRUE
    )

@@

core.did.estimates %>% 
  kable("html", booktabs = T, col.names = c("Outcome","Estimate","95% CI")) %>% 
  kable_styling(latex_options = c("striped")) %>%
  pack_rows(index = c("Overall Impacts" = 4, "Quality of Care" = 6, "Patient Complexity" = 2, "Payer Mix" = 4, "Finances" = 6)) %>% 
  add_header_above(c("IV-Estimated LATE Effects of Competitive Shocks on Incumbent Clinics" = 3))

@@

## TWFE First Stage
df.temptemptemp <- df.temptemp %>% select(ClinicHHI, Qcomp, MS, value, Year, ID, Pct.NHA:Pct.None) %>% ungroup() %>% filter(complete.cases(.))

@@

model <- lm(data = df.temptemptemp, Qcomp ~ firststage$fitted.values + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless)

@@

@@

```{r}
df.temptemp %>% #left_join(df.temptemp %>% filter(Tx == 1) %>% summarise(Att = min(Year)), by = c("ID")) %>% 
               mutate(Att = ifelse(is.na(Att), 0, Att)) %>% 
  mutate(value = ifelse(value >= 6, 6, value)) %>% 
  group_by(value, Year) %>% 
  summarise(HHI = mean(ClinicHHI, na.rm = TRUE)) %>% 
  ggplot(aes(x = Year, y = HHI, group = value, color = as.factor(value))) + geom_point() + geom_line()
```

@@

@@

df.z.temp <- df.z %>% mutate(Tx = ifelse(value - 1 > 1, 1, value - 1)) %>% filter(!is.na(Tx)) %>% mutate(DirectlyTreated = ifelse(Att.z > 2010, 1, 0)) %>% 
  filter(!(Att == 0 & DirectlyTreated == 1)) %>% 
        mutate(Pct.MCD = Medicaid / NumberofPatients * 100, 
               Pct.MCR = Medicare / NumberofPatients * 100, 
               Pct.COM = Private / NumberofPatients * 100,
               Pct.None = Uninsured / NumberofPatients * 100 ) %>% 
  select(NumberofPatients, Pct.MCD:Pct.None, Total.Hours, Sites, Mean.Hours, Perminance, Schedule, Calendar, Tx, DirectlyTreated, ID, Year, Zip, Att, `BHCMIS ID`)

@@

```{r}
 event_study(data = df.z.temp %>% filter(Att == 0 | DirectlyTreated == 0),
  yname = "Total.Hours", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~1) %>%
  filter(abs(term) <= 6) %>%
  filter(estimator == "Gardner (2021)") %>%
  #filter(estimator == "Callaway and Sant'Anna (2020)") %>%
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")

 event_study(data = df.z.temp %>% filter(Att == 0 | DirectlyTreated == 1),
  yname = "Total.Hours", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~1) %>%
  filter(abs(term) <= 6) %>%
  filter(estimator == "Gardner (2021)") %>%
  #filter(estimator == "Callaway and Sant'Anna (2020)") %>%
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")

@@

>>>>

df.temptemp <- df.mt %>% 
    rename(ID = ID.x) %>% 
    group_by(ID) %>% 
  mutate(Closed = ifelse(lead(is.na(Sites)), 100, 0)) %>% 
  select(ClinicHHI, Att, `BHCMIS ID`, value, ID, MS, Year, Pct.NHA:Pct.Homeless, Qcomp, Total, Altman, logPatsPerStaff, 
         htn.rate, dm.rate, pap.rate, crc.rate, childbmi.rate, adultbmi.rate, Complexity, Intensity, Pct.MCD, Pct.MCR, Pct.COM, Pct.None, CostPerPat, quick_ratio, months_of_cash, Profitability, LiabPctAssets, Staff, Closed, pap.denom, crc.denom, childbmi.denom, adultbmi.denom, htn.total, dm.total, asthma.rate, cad.rate, ivd.rate, ngla_net_gain_loss, Liquidity, Efficiency, NetWorth, Liabilities) %>% 
  unique()

@@

# df.temptemp <- df.temptemp %>% 
#   left_join(uds.cw %>% filter(Year == 2011) %>% select(BHCMIS.ID:PH), by = c("BHCMIS ID" = "BHCMIS.ID")) %>% 
#   mutate(ACA = ifelse((STATE %in% c('MI','NH') & Year >= 2014) |
#                     (STATE %in% c('PA','IN','AK') & Year >= 2015) |
#                     (STATE %in% c('MT','LA') & Year >= 2016) |
#                     (STATE %in% c('VA','ME') & Year >= 2019) |
#                     (STATE %in% c('ID','UT','NE') & Year >= 2020) |
#                     (STATE %in% c('OK','MO') & Year >= 2021) |
#                     (STATE %in% c('AZ','AR','CA','CO','CT','DE','DC','HI','IL','IA','KY','MD','MA','MN','NV','NJ','NM','NY','ND','OH','OR','PA','RI','VT','VA','WA') & Year >= 2014), 1, 0))

@@

for (k in 1:28){

  df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx))
  colnames(df.temptemptemp)[(16+k)] <- "Outcome"
  #model <- feols(Outcome ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless   | I((10000 - ClinicHHI)/1000) ~ Tx + factor(Year) + factor(ID) , cluster = "ID", data = df.temptemptemp)
  #coeffs <- rbind(coeffs, model$coeftable[2,])
  model <- feols(Outcome ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + MHC + HO + PH | ID + Year | I((10000 - ClinicHHI)/1000) ~ value, cluster = "ID", data = df.temptemptemp)
  coeffs <- rbind(coeffs, model$coeftable[1,])

@@

core.iv.estimates <- data.frame(cbind(colnames(df.temptemp)[17:44], (coeffs[-1,]))) %>% 
  #select(V1, Estimate, Pr...t.., Estimate.1, Pr...t...1) %>% 
  mutate(Estimate = round(as.numeric(Estimate), 2), `95% CI` = paste(round(as.numeric(Estimate) - 1.96 * as.numeric(`Std..Error`), 2), ", ", round(as.numeric(Estimate) + 1.96 * as.numeric(`Std..Error`), 2), sep = "")) %>% 
  select(V1, Estimate, `95% CI`)

@@

summary(feols(df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)), I( Pct.None  ) ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year | I((10000 - ClinicHHI)/100) ~ Tx, cluster = "ID"))

@@

```{r}
 did2s(
      data = df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)  ) , 
      yname = "ClinicHHI", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = TRUE
    )

    event_study(data = df.temptemp,
  yname = "ClinicHHI", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>%
  filter(abs(term) <= 6) %>%
  filter(estimator == "Gardner (2021)") %>%
  #filter(estimator == "Callaway and Sant'Anna (2020)") %>%
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("FirstStage: ") + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")

## Heterogeneity by Starting Point
```{r}

 event_study(data = df.temptemp %>% filter(value_min == 1),
  yname = "Qcomp", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>%
  filter(abs(term) <= 6) %>%
  filter(estimator == "Gardner (2021)") %>%
  #filter(estimator == "Callaway and Sant'Anna (2020)") %>%
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("FirstStage: ") + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")

 event_study(data = df.temptemp,
  yname = "Qcomp", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>%
  filter(abs(term) <= 8) %>%
  filter(estimator == "Gardner (2021)") %>%
  #filter(estimator == "Callaway and Sant'Anna (2020)") %>%
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("FirstStage: ") + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")

  event_study(data = df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) %>% mutate(Att = ifelse(Att == 2010, 0, Att)),
  yname = "Staff", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>%
  filter(abs(term) <= 8) %>%
  filter(estimator == "Gardner (2021)") %>%
  #filter(estimator == "Callaway and Sant'Anna (2020)") %>%
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("FirstStage: ") + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")

@@

  df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) #%>% group_by(ID) %>% mutate(EarlyHHI = first(ClinicHHI, na_rm = TRUE)) %>% filter(EarlyHHI < 9000)
  colnames(df.temptemptemp)[(16+k)] <- "Outcome"
  model <-  did2s(
      data = df.temptemptemp, 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = TRUE
    )

@@

core.did.estimates %>% 
  kable("html", booktabs = T, col.names = c("Outcome","Estimate","95% CI")) %>% 
  kable_styling(latex_options = c("striped")) %>%
  pack_rows(index = c("Overall Impacts" = 4, "Quality of Care" = 6, "Patient Complexity" = 2, "Payer Mix" = 4, "Finances" = 6)) %>% 
  add_header_above(c("DID-Estimated Effects of Competitive Shocks on Incumbent Clinics" = 3))

did2s(
      data = df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) %>% mutate(Mix = Pct.COM * Total / 100) %>% filter(Year < 2020 ), 
      yname = "Closed", 
      treatment = "Tx",
        first_stage = ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = TRUE
    )

df.temptemp %>% 
    ungroup() %>% 
  group_by(Tx) %>% 
  summarise(mean(Qcomp, na.rm = TRUE))

@@

## TWFE First Stage
df.temptemptemp <- df.temptemp %>% select(ClinicHHI, Qcomp, MS, value, Year, ID, Pct.NHA:Pct.None, Tx) %>% ungroup() %>% filter(complete.cases(.))

@@

model <- lm(data = df.temptemptemp, Complexity ~ firststage$fitted.values + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless+ factor(Year) + factor(ID))

@@

## Basic Linear Reg
```{r}

reduced <- lm(data = df.temptemptemp, Qcomp ~ value + factor(Year) + factor(ID) + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless )
head(summary(reduced)$coeff) %>% as.data.frame()

reduced <- lm(data = df.temptemptemp, Complexity ~ value + factor(Year) + factor(ID) + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless )
head(summary(reduced)$coeff) %>% as.data.frame()

reduced <- lm(data = df.temptemptemp, Closed ~ value + factor(Year) + factor(ID) + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless )
head(summary(reduced)$coeff) %>% as.data.frame()

@@

```{r}
df.temptemp %>% #left_join(df.temptemp %>% filter(Tx == 1) %>% summarise(Att = min(Year)), by = c("ID")) %>% 
               mutate(Att = ifelse(is.na(Att), 0, Att)) %>% 
  mutate(value = ifelse(value >= 6, 6, value)) %>% 
  group_by(value, Year) %>% 
  summarise(HHI = mean(ClinicHHI, na.rm = TRUE)) %>% 
  ggplot(aes(x = Year, y = HHI, group = value, color = as.factor(value))) + geom_point() + geom_line()

df.temptemp %>% #left_join(df.temptemp %>% filter(Tx == 1) %>% summarise(Att = min(Year)), by = c("ID")) %>% 
               mutate(Att = ifelse(is.na(Att), 0, Att)) %>% 
  mutate(value = ifelse(value >= 6, 6, value)) %>% 
  group_by(value, Year) %>% 
  summarise(Quality = mean(Qcomp, na.rm = TRUE)) %>% 
  ggplot(aes(x = Year, y = Quality, group = value, color = as.factor(value))) + geom_point() + geom_line()
```

@@

df.temptemp %>% 
  filter(Year == 2023) %>% 
  mutate(Treat = ifelse(Att > 0, "Treated", "Control")) %>% 
  select(Treat, Total, Pct.NHA:Staff) %>% 
  ungroup() %>% 
  summarise(n(), sum(Total, na.rm = TRUE))

@@

df.z.temp <- df.z %>% mutate(Tx = ifelse(value - 1 >= 1, 1, value - 1)) %>% filter(!is.na(Tx)) %>% mutate(DirectlyTreated = ifelse(Att.z >= 2010, 1, 0)) %>% 
  #df.z %>% mutate(Tx = ifelse(value - 1 > 1, 1, value - 1)) %>% filter(!is.na(Tx)) %>% mutate(DirectlyTreated = ifelse(Att.z > 2010, 1, 0)) %>% 
  filter(!(Att == 0 & DirectlyTreated == 1)) %>% 
        mutate(Pct.MCD = Medicaid / NumberofPatients * 100, 
               Pct.MCR = Medicare / NumberofPatients * 100, 
               Pct.COM = Private / NumberofPatients * 100,
               Pct.None = Uninsured / NumberofPatients * 100 ) %>% 
  select(NumberofPatients, Pct.MCD:Pct.None, Total.Hours, Sites, Mean.Hours, Perminance, Schedule, Calendar, Tx, DirectlyTreated, ID, Year, Zip, Att, `BHCMIS ID`)

@@

```{r}
 event_study(data = df.z.temp %>% filter(Att == 0 | (Att > 0 & DirectlyTreated == 0)),
  yname = "Total.Hours", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~1) %>%
  filter(abs(term) <= 8) %>%
  filter(estimator == "Gardner (2021)") %>%
  #filter(estimator == "Callaway and Sant'Anna (2020)") %>%
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")

 event_study(data = df.z.temp %>% filter(Att == 0 | (Att > 0 & DirectlyTreated == 1)),
  yname = "Total.Hours", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~1) %>%
  filter(abs(term) <= 8) %>%
  filter(estimator == "Gardner (2021)") %>%
  #filter(estimator == "Callaway and Sant'Anna (2020)") %>%
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")

@@

## Auditing

df.z.temp %>% 
  select(`BHCMIS ID`, Year, Zip, Att, DirectlyTreated)

uds.sites.full %>% 
  filter(Zip == "02301") %>% 
  select(Year, `BHCMIS ID`) %>% 
  unique() %>% 
  filter(Year >= 2010) %>% 
  arrange(Year, `BHCMIS ID`)

df.z %>% mutate(Tx = ifelse(value - 1 >= 1, 1, value - 1)) %>% filter(!is.na(Tx)) %>% mutate(DirectlyTreated = ifelse(Att.z >= 2010, 1, 0))

# Distance Intrustment

## Treatment vs control, only in zip code of interest
df.z <- left_join(df.temptemp, 
                  #uds.zip %>% mutate(Zip = `ZipCode`) %>% select(`BHCMISID`, Zip) %>% unique() , by = c("BHCMIS ID" = "BHCMISID")) %>%
                  uds.sites.full[!is.na(uds.sites.full$Zip),] %>% filter(Year %in% c(2010:2021)) %>% select(`BHCMIS ID`, Zip) %>% unique() %>% filter(!is.na(Zip)), by = c("BHCMIS ID")) %>%
  left_join(uds.zip, by = c("BHCMIS ID" = "BHCMISID", "Year" = "ReportingYear", "Zip" = "ZipCode")) %>%
  filter(!is.na(GrantNumber)) %>% 
  left_join(clinics.in.zips %>% select(Zip:Clinics), by = c("Zip","Year")) %>%
  mutate(Tx.z = ifelse(Clinics == 1 , 0, 
                ifelse(is.na(Clinics), NA, 1)), # | is.na(Clinics)
         ID = as.numeric(factor(paste(`BHCMIS ID`, Zip, sep = "-")))) %>%
  select(`BHCMIS ID`:Year, Att, ID, Zip:Tx.z, Tx) %>%
  arrange(`BHCMIS ID`, Zip, Year) %>% 
  unique() #%>%  inner_join(df.qual.exp %>% filter(Year == 2015 & Total > 12050) %>% select(`Grant Number`), by = c("Grant Number"))  #& Zips < 3.75 or 4.75
  # %>%   filter(MarketShare > median(MarketShare, na.rm = TRUE) - 0.25)

## Whole zip as one measure

df.z.full <- df.z %>% ############## NOTE: Original +500 effect was recoved with Att.z, not Att
  select(Zip, Att.z, Year) %>% 
  unique() %>% 
  left_join(uds.zip, by = c("Zip" = "ZipCode", "Year" = "ReportingYear")) %>% 
  left_join(df.temptemp %>% 
            select(`BHCMIS ID`, Year, Qcomp), by = c("BHCMISID" = "BHCMIS ID", "Year")) %>% 
  group_by(Zip, Year, Att.z) %>% 
  summarise(
    Total.z = sum(NumberofPatients, na.rm = TRUE), 
    Quality.z = sum(NumberofPatients * Qcomp, na.rm = TRUE) / Total.z) %>% 
  ungroup() %>% 
  mutate(ID = as.numeric(as.factor(Zip)))# %>% group_by(`Grant Number`, Year, Att) %>% summarise(ID = min(ID), Total.z = sum(Total.z, na.rm = TRUE)) # %>% filter(Year > 2015),

df.zip.1 <- df.z %>% select(ID, Year, Att, NumberofPatients)
df.zip.2 <- df.z.full %>% select(ID, Year, Att.z, Total.z:Quality.z)

## Edit Centroids

```{r}
## Read in Centroid Data
zip.centroids <- read.csv("/Users/markow/Dropbox/Git/Data/ZIP_Code_Population_Weighted_Centroids.csv") %>% 
  mutate(ZipCode = str_pad(STD_ZIP5, 5, pad = "0")) %>% 
  select(ZipCode, X, Y)
## Add missing centroids
zip.centroids <- rbind(zip.centroids, c(ZipCode = "37243", X = -86.783, Y = 36.165), 
                                      c(ZipCode = "95951", X = -121.98, Y = 39.73), 
                                      c(ZipCode = "99733", X = -144.166941, Y = 65.799773),

                                      c(ZipCode = "04341", X = -69.4277, Y = 55.3255), 
                                      c(ZipCode = "04935", X = -69.5995, Y = 44.5884)
                      ) %>% 
  mutate(X = as.numeric(X), Y = as.numeric(Y))
```

## Describe where the rivals came from
```{r}

## Distance of Competitor to New Site
df.z.dist <- df.z.full %>% 
  filter(Att.z == Year) %>% 
  select(Zip:Total.z) %>% 
  left_join(uds.sites.full %>% select(`BHCMIS ID`, Year, Zip) %>% unique(), by = c("Zip","Year")) %>% 
  left_join(df.z %>% filter(Tx == 1) %>% select(`BHCMIS ID`, Year, Zip) %>% unique(), by = c("Zip","Year")) %>% 
  filter(`BHCMIS ID.x` != `BHCMIS ID.y`)

df.z.dist <- df.z.dist %>% mutate(DistToClosestSite = NA, ZipOfClosestSite = NA)

for (g in 1:nrow(df.z.dist)){
#g <- 1
 temp <- rbind(zip.centroids %>% filter(ZipCode == df.z.dist[g,]$Zip), 
          zip.centroids %>% filter(ZipCode %in% unique(uds.sites.full[uds.sites.full$`BHCMIS ID` == df.z.dist[g,]$`BHCMIS ID.x` & uds.sites.full$Year == df.z.dist[g,]$Year,]$Zip))) %>% 
   unique()
  mm <- as.matrix(dist(as.matrix(temp$X, temp$Y), method = "euclidean"))[-1,1]
  df.z.dist[g,]$DistToClosestSite <-  min(mm) * 111.139
  df.z.dist[g,]$ZipOfClosestSite  <- ifelse(is.na(temp[2,]$ZipCode), temp[1,]$ZipCode, unlist(temp[-1,]$ZipCode[rank(mm) == 1]))
}

#df.z.dist[19,]$DistToClosestSite <- 0
df.z.dist <- df.z.dist %>% 
  filter(!is.infinite(DistToClosestSite))

df.z.dist <- df.z.dist %>% 
  inner_join(df.z.dist %>% group_by(`BHCMIS ID.y`) %>% summarise(Att.z = min(Att.z)), by = c("BHCMIS ID.y", "Att.z")) %>% 
  unique()

mean(df.z.dist$DistToClosestSite)
quantile(df.z.dist$DistToClosestSite, probs = c(0, 0.1, 0.25, 0.5, 0.75, 0.9, 1))

# mean(df.z.dist[df.z.dist$ZipFilter == 1,]$DistToClosestSite)
# mean(df.z.dist[df.z.dist$ZipFilter == 2,]$DistToClosestSite)
# 
# quantile(df.z.dist[df.z.dist$ZipFilter == 1,]$DistToClosestSite, probs = c(0, 0.1, 0.25, 0.5, 0.75, 0.9, 1))
# quantile(df.z.dist[df.z.dist$ZipFilter == 2,]$DistToClosestSite, probs = c(0, 0.1, 0.25, 0.5, 0.75, 0.9, 1))

zipsize <- zctas(starts_with = c(df.z.dist$Zip, df.z.dist$ZipOfClosestSite), year = 2010)

## Original Figure
df.z.dist.plot <- df.z.dist %>% 
  left_join(zipsize %>% select(GEOID10, ALAND10), by = c("Zip" = "GEOID10")) %>% 
  left_join(uds.sites.full %>% select(Zip, `Site State`) %>% unique(), by = c("Zip")) %>% 
  left_join(census %>% select(ZipCode, YEAR, TotalPop), by = c("Year" = "YEAR", "Zip" = "ZipCode")) %>% 
  arrange(desc(DistToClosestSite)) %>% 
  mutate(Area.SQmiles = ALAND10 / 2.59e6) %>% 
  mutate(Density.NewZip = TotalPop / Area.SQmiles, 
         l.density = log(TotalPop / Area.SQmiles)) %>% 
  unique()

df.z.dist.plot %>% 
  ggplot(aes(x = log(Density.NewZip), y = DistToClosestSite)) + geom_point(aes(size = Area.SQmiles)) +
  ggtitle("Distance from Rival's newly competing zip ocde to closest incumbent zip code by Density and Area of newly competing zip code")

summary(lm(DistToClosestSite ~ log(Density.NewZip), data = df.z.dist.plot))
